\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-24 papers/jss/article.Rnw
Improve section 7 and update the conclusions to note we've been using this package at Google for 5 years, not 3 years.  Done with section 7 updates.  6 and 8 need work.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@904 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Protocol Buffers have been used extensively at Google for almost all
RPC protocols, and for storing structured information in a variety of
persistent storage systems since 2000 \citep{dean2009designs}.  The
\pkg{RProtoBuf} package has been in widespread use by hundreds of
analysts at Google since 2010.

@@

One of the authors has used this design pattern for several
large-scale studies of distributed storage systems
\citep{sciencecloud,janus}.

@@

The \pkg{RProtoBuf} package builds on the Protocol Buffers \proglang{C++} library, 
and extends the \proglang{R} system with the ability to create, read,
write, parse, and manipulate Protocol
Buffer messages. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts, and software engineers.
At the time of this writing there are over 300 active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with distributed systems written in \proglang{C++}, \proglang{Java}, \proglang{Python}, and 
other languages. We hope that making Protocol Buffers available to the
\proglang{R} community will contribute towards better software integration
and allow for building even more advanced applications and analysis pipelines 
with \proglang{R}.

>>>>

Protocol Buffers have been used extensively at Google for almost all
RPC protocols, and for storing structured information in a variety of
persistent storage systems since 2000 \citep{dean2009designs}.  The
\pkg{RProtoBuf} package has been in widespread use by hundreds of
statisticians and software engineers at Google since 2010.  This
section describes a simplified example of a common design pattern of
collecting a large structured data set in one language for later
analysis in \proglang{R}.

@@

One of the authors has used this design pattern with large-scale \proglang{C++}
MapReduces over very large data sets to write out histogram protocol
buffers for several large-scale studies of distributed storage systems
\citep{sciencecloud,janus}.

@@

The \pkg{RProtoBuf} package builds on the Protocol Buffers \proglang{C++} library, 
and extends the \proglang{R} system with the ability to create, read,
write, parse, and manipulate Protocol
Buffer messages. \pkg{RProtoBuf} has been used extensively inside Google 
for the past five years by statisticians, analysts, and software engineers.
At the time of this writing there are over 300 active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with distributed systems written in \proglang{C++}, \proglang{Java}, \proglang{Python}, and 
other languages. We hope that making Protocol Buffers available to the
\proglang{R} community will contribute towards better software integration
and allow for building even more advanced applications and analysis pipelines 
with \proglang{R}.
